One Year HPC Certification Forum in Retrospective

### 2019-04-17 paper.tex
Resolved some low-hanging fruits.

\newcommand{\jk}[1]{\todo[inline]{TODO: #1}}
\newcommand{\ag}[1]{\todo[inline]{IDEA: #1}}
\newcommand{\kh}[1]{\todo[inline]{KH: #1}}

@@

\paragraph{Technical}\kh{"Management" (oberhalb) finde ich auf der Ebene alleinstehend gut, "Technical" etwas zu kurz, Vorschlag: "Technical Tasks" (o.ä.)}
According to our goals, we address 1) the definition of competencies; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.

@@

Next, we present a generic skill that describes an inner-node in more details.
\ag{change sentence because delivery and deliver in one sentence -
There is no actual delivery as a module or teaching event to deliver the content, it serves the purpose to inform the practitioner about the importance of the skill.
}
\begin{itemize}
  \item \textbf{ID}: USE4.2-B
  \item \textbf{Name}: Executing parallel applications
  \item \textbf{Background}:
  Parallel computers are operated differently than a normal PC, all users must share the system. Therefore, various operative procedures are in place. Users must understand these concepts and procedures to be able to use the available resources of a system to run a parallel application. Moreover, individual solutions can often be found in a specific system.
  \item \textbf{Aim}: To enable practitioners to comprehend the concepts and procedures for running parallel applications in HPC environments.
  To use the system to run and monitor the execution of parallel applications on the HPC system.

@@

The following skill describes a leaf-level skill for the usage of Slurm in\kh{at} the basic level.
While there is no formal dependency to the introduction (skill USE4.2.2-B), it is expected that practitioners have obtained the other skill before learning this one.

\begin{itemize}
  \item \textbf{ID}: USE4.2.2-B
  \item \textbf{Name}: Slurm Workload manager
  \item \textbf{Background}: Slurm is a widely used open-source workload manager providing various advanced features\kh{Vorschlag: einige der Highlights anführen: "... , like ..."}.
  \item \textbf{Aims}:
  \begin{itemize}
    \item To enable practitioners to use relevant tools to run and monitor parallel applications using Slurm.
    \item To enable practitioners to comprehend and describe the basic architecture of Slurm and the suite of tools.
  \end{itemize}
  \item \textbf{Learning outcomes}:
  \begin{itemize}
  \item run interactive jobs with salloc, a batch job with sbatch
  \item explain the architecture of Slurm, i.e., the role of Slurmd\kh{Slurmd haben wir beim "Basic Level" bisher nicht vorgesehen}, srun and the injection of environment variables
  \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
  \item explain time limits and the benefit of a backfill scheduler
  \item comprehend that environment variables are set when running a job
  \item comprehend and describe the expected behavior of a simple job scripts\kh{typo?}
  \item comprehend how variables are prioritized when using command line and a script
  \item change a provided job template and embed them into shell scripts to run a variety of parallel applications
  \item analyze the output generated from submitting to the job scheduler and typically generated errors
  \end{itemize}
\end{itemize}

@@

Firstly, an author of training material is allowed to indicate on the training material itself or on promotional material the fact
which skills are covered by the material completely or partially.
We provide a seal that can be used for that purpose (see \Cref{fig:seal-teaching}).
The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material
registers a link to the material or course and their\kh{Plural hier beabsichtigt (Bezug?)} email address on our webpage using an online form.
That way, the HPCCF is informed about the usage of the seal.

>>>>

\newcommand{\jk}[1]{\todo[inline]{JK: #1}}
\newcommand{\ag}[1]{\todo[inline]{Anja: #1}}
\newcommand{\kh}[1]{\todo[inline]{KH: #1}}

@@

\paragraph{Technical tasks}
According to our goals, we address 1) the definition of competencies; 2) the creation of certificates; 3) the examination of practitioners; and 4) an ecosystem of tools supporting them.

@@

Next, we present a generic competence that describes an inner-node of the skill tree in more details.

\begin{itemize}
  \item \textbf{ID}: USE4.2-B
  \item \textbf{Name}: Executing parallel applications
  \item \textbf{Background}:
  Parallel computers are operated differently than a normal PC, all users must share the system. Therefore, various operative procedures are in place. Users must understand these concepts and procedures to be able to use the available resources of a system to run a parallel application. Moreover, individual solutions can often be found in a specific system.
  \item \textbf{Aim}: To enable practitioners to comprehend the concepts and procedures for running parallel applications in HPC environments.
  To use the system to run and monitor the execution of parallel applications on the HPC system.

@@

The following skill describes a leaf-level skill for the usage of Slurm at the basic level.
While there is no formal dependency to the introduction (skill USE4.2.2-B), it is expected that practitioners have obtained the other skill before learning this one.

\begin{itemize}
  \item \textbf{ID}: USE4.2.2-B
  \item \textbf{Name}: Slurm Workload manager
  \item \textbf{Background}: Slurm is a widely used open-source workload manager providing various advanced features. % \kh{Vorschlag: einige der Highlights anführen: "... , like ..."}. Good idea, but later!
  \item \textbf{Aims}:
  \begin{itemize}
    \item To enable practitioners to use relevant tools to run and monitor parallel applications using Slurm.
    \item To enable practitioners to comprehend and describe the basic architecture of Slurm and the suite of tools.
  \end{itemize}
  \item \textbf{Learning outcomes}:
  \begin{itemize}
  \item run interactive jobs with salloc, a batch job with sbatch
  \item explain the architecture of Slurm, i.e., the role of Slurmd, srun and the injection of environment variables
  \item explain the function of the tools: sacct, sbatch, salloc, srun, scancel, squeue, sinfo
  \item explain time limits and the benefit of a backfill scheduler
  \item comprehend that environment variables are set when running a job
  \item comprehend and describe the expected behavior of a simple job script
  \item comprehend how variables are prioritized when using command line and a script
  \item change a provided job template and embed them into shell scripts to run a variety of parallel applications
  \item analyze the output generated from submitting to the job scheduler and typically generated errors
  \end{itemize}
\end{itemize}

@@

Firstly, an author of training material is allowed to indicate on the training material itself or on promotional material the fact
which skills are covered by the material completely or partially.
We provide a seal that can be used for that purpose (see \Cref{fig:seal-teaching}).
The reference to the HPCCF and the seal can be used free of charge under the condition that the developer of the training material
registers a link to the material or course on our webpage using an online form. %\footnote{Details of the link will show the email address.}
That way, the HPCCF is informed about the usage of the seal.
